DATA 621---Business Analytics and Data Mining

### 2020-09-19 HW1/HW1_draft_kellogg.Rmd
Updated Model 3 coef discussion

Studying the coefficients of the model suggest that winning is in favor if the
team batting hits more doubles, triples and home runs. Moreover, increase in the
number of stolen bases, and a decrease in caught steals, double plays, error,
and walks allowed would all lead to a win for the batting team. It is noteworthy
that the model suggests that a decrease in single hits by batter and an increase
in strikeouts by batters which seems counter intuitive. But these variables were
kept because when a batter steps to the plate, the player is more likely to
strike out than to get a hit. Trying to hit the ball out of the park will come
with strikeouts but it will also increase the chances of hitting home runs (even
1B, 2B, 3B), and that is pretty good exchange that most teams are willing carry
out.

>>>>

From studying each coefficient, this discussion begins with the variables that follow 
the logic of winning and are self-evident. Firstly, the model suggests that winning is 
in favor of the team batting hits more bases, (1B, 2B, 3B, HR). It further reveals that 
an increase in singles would lead to better chances of winning. A hit is a hit, and more 
hits than the opponent will inevitably lead to a win. Likewise, an increase in walks by 
the batting team is awarded first base, further increasing base counts and, thus the 
chances of winning. In terms of the base run, an increase in the number of stolen bases, 
and a decrease in caught steals would lead to a win for the batting team. These variables 
have a positive effect on the number of wins, and it is understandable as to why.

When interpreting the model based on the pitching team's plays, it is perceptible that 
walks allowed should be reduced so that the batting team hits does not increase. Moreover, 
preventing errors and increasing double plays in which two players are put out will also 
increase the chances of winning.

On the other hand, it is noteworthy that the model suggests some counter-intuitive play 
strategies. Firstly, when all variables are null, the intercept predicts that a team would 
win, with a target win of 129. Moreover, the model suggests that a decrease in double hits 
and an increase in strikeouts by the batting team will improve winning. These variables 
were kept because when a batter steps to the plate, the player is more likely to strike 
out than to get a hit. Trying to hit the ball out of the park will come with strikeouts 
but it will also increase the chances of hitting home runs (even 1B, 2B, 3B), and that is 
a pretty good exchange that most teams are willing to perform.
